### 2013-07-23 doc/asplos14/conclude.tex
reworded confusing sentance

Our evaluation of \Grappa reveals that the core components, scheduling and communication, achieve their design goals.  Thousands of workers can be efficiently context switched on a multicore processor, up to the DRAM bandwidth.  Aggregating messages enables \Grappa to achieve over 1.0 GUPS on 64 nodes.  We also explored four other algorithms: unbalanced tree search, breadth first search, PageRank, and integer sort, comparing performance of these algorithms on \Grappa, the Cray XMT, and hand-optimized MPI implementations.  As would be expected, when the MPI implementation exploits in the application, many of the same techniques \Grappa provides in the runtime, such as aggregating requests, yet without the overhead of tasking, the MPI implementation excels.  This comes with enormous implementation complexity, burdening the application developer. Moreover, significant tuning has yet to be done on the \Grappa runtime system.  Compared to the Cray XMT \Grappa is between 2.6X faster and 4.3X slower.  Yet when cost-performance is considered, mass-market x86 cluster hardware makes \Grappa a highly attractive option.

>>>>

Our evaluation of \Grappa reveals that the core components, scheduling
and communication, achieve their design goals.  Thousands of workers
can be efficiently context switched on a multicore processor, up to
the DRAM bandwidth.  Aggregating messages enables \Grappa to achieve
over 1.0~GUPS on 64~nodes.  We also explored four other algorithms:
unbalanced tree search, breadth first search, PageRank, and integer
sort, comparing performance of these algorithms on \Grappa, the Cray
XMT, and hand-optimized MPI implementations.  As might be expected,
when an MPI implementation exploits, in the application code, many of the
same techniques \Grappa provides in the runtime, such as aggregating
requests, yet without the overhead of tasking, the MPI implementation
excels.  This comes with enormous implementation complexity, burdening
the application developer. Moreover, significant tuning has yet to be
done on the \Grappa runtime system.  Compared to the Cray XMT, \Grappa
is between 2.6X faster and 4.3X slower.  Yet when cost-performance is
considered, mass-market x86-based cluster hardware makes \Grappa a
highly attractive option.
